%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Jessica}{Burnett}

\address{5067 6th Place NE, Washington, D.C. 20017}

\email{\href{mailto:jessica.burnett@nasa.gov}{\nolinkurl{jessica.burnett@nasa.gov}}}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {March 2023}
    {Jessica Burnett~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{research-interests}{%
\section{Research Interests}\label{research-interests}}

Attention; distraction; mind-wandering; eye movements

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Postdoctoral Research Fellow, Department of Psychology}{University of Michigan}{Ann Arbor, MI, USA}{06/2020-present}{\begin{cvitems}
\item Advisor: Dr. John Jonides
\end{cvitems}}
    \cventry{Doctor of Philosophy, Education and Psychology}{University of Michigan}{Ann Arbor, MI, USA}{09/2014-05/2020}{\begin{cvitems}
\item Dissertation: Mind-wandering: What Can We Learn from Eye Movements?
\end{cvitems}}
    \cventry{Master of Science, Psychology}{University of Michigan}{Ann Arbor, MI, USA}{09/2014-04/2018}{}\vspace{-4.0mm}
    \cventry{Bachelor of Science, Psychology}{Beijing Normal University}{Beijing, China}{09/2010-07/2014}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{awards-and-grants}{%
\section{Awards and Grants}\label{awards-and-grants}}

\begin{cventries}
    \cventry{School of Education, University of Michigan}{Stanley E. and Ruth B. Dimond Best Dissertation Award}{2020}{}{\begin{cvitems}
\item Dissertation: Mind-wandering: What Can We Learn from Eye Movements?
\end{cvitems}}
    \cventry{School of Education, University of Michigan}{2020 ProQuest Distinguished Dissertation Awards (Nomination)}{2020}{}{\begin{cvitems}
\item Dissertation: Mind-wandering: What Can We Learn from Eye Movements?
\end{cvitems}}
    \cventry{Rackham Graduate School, University of Michigan}{Rackham One-Term Dissertation Fellowship}{2019}{\$17417}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School, University of Michigan}{Rackham Graduate Student Research Grant}{2019}{\$3000}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School, University of Michigan}{Rackham Conference Travel Grant}{2019, 2018, 2017}{\$1050}{}\vspace{-4.0mm}
    \cventry{Rackham Graduate School, University of Michigan}{Rackham Summer Training Award}{2018}{\$3700}{}\vspace{-4.0mm}
    \cventry{School of Education, University of Michigan}{Professor \& Mrs. Cho-Yee To Travel Grant}{2017, 2015}{\$500}{}\vspace{-4.0mm}
    \cventry{Ministry of Education of the People's Republic of China}{China National Scholarship}{2014}{\$1500}{}\vspace{-4.0mm}
    \cventry{Faculty of Psychology, Beijing Normal University}{The First Rank Academic Scholarship}{2014, 2013}{\$300}{}\vspace{-4.0mm}
    \cventry{Beijing Municipal Commission of Education}{Beijing Student Research and Entrepreneurial Action Plan}{2013}{\$1500}{}\vspace{-4.0mm}
    \cventry{Faculty of Psychology, Beijing Normal University}{Undergraduate Student Research Grant}{2012}{\$280}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{peer-reviewed-publications}{%
\section{Peer-reviewed Publications}\label{peer-reviewed-publications}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-halpern2023priorities}{}}%
Halpern, B. S., Boettiger, C., Dietze, M. C., Gephart, J. A., Gonzalez,
P., Grimm, N. B., Groffman, P. M., Gurevitch, J., Hobbie, S. E.,
Komatsu, K. J., et al. (2023). Priorities for synthesis research in
ecology and environmental science. \emph{Ecosphere}, \emph{14}(1),
e4342.

\leavevmode\vadjust pre{\hypertarget{ref-burnett2021ten}{}}%
Burnett, J. L., Dale, R., Hou, C.-Y., Palomo-Munoz, G., Whitney, K. S.,
Aulenbach, S., Bristol, R. S., Valle, D., \& Wellman, T. P. (2021). Ten
simple rules for creating a scientific web application. \emph{PLOS
Computational Biology}, \emph{17}(12), e1009574.

\leavevmode\vadjust pre{\hypertarget{ref-erickson2021paths}{}}%
Erickson, R. A., Burnett, J. L., Wiltermuth, M. T., Bulliner, E. A., \&
Hsu, L. (2021). Paths to computational fluency for natural resource
educators, researchers, and managers. \emph{Natural Resource Modeling},
\emph{34}(3), e12318.

\leavevmode\vadjust pre{\hypertarget{ref-allen2019serdp}{}}%
Allen, C., Burnett, J. L., Roberts, C. P., Twidwell, D., \& Angeler, D.
G. (2019). \emph{SERDP project RC-2510: Global change, vulnerability and
resilience: Management options for an uncertain future}.

\leavevmode\vadjust pre{\hypertarget{ref-burnett2019regime}{}}%
Burnett, J. L. (2019). \emph{Regime detection measures for the practical
ecologist} {[}PhD thesis{]}. University of Nebraska-Lincoln.

\leavevmode\vadjust pre{\hypertarget{ref-burnett2019bbsassistant}{}}%
Burnett, J. L., Wszola, L., \& Palomo-Muñoz, G. (2019). bbsAssistant: An
r package for downloading and handling data and information from the
north american breeding bird survey. \emph{Journal of Open Source
Software}, \emph{4}(44), 1768.

\leavevmode\vadjust pre{\hypertarget{ref-roberts2018early}{}}%
Roberts, C. P., Twidwell, D., Burnett, J. L., Donovan, V. M., Wonkka, C.
L., Bielski, C. L., Garmestani, A. S., Angeler, D. G., Eason, T.,
Allred, B. W., Jones, M. O., Naugle, D. E., Sundstrom, S. M., \& Allen,
C. R. (2018). Early warnings for state transitions. \emph{Rangeland
Ecology \& Management}, \emph{71}(6), 659--670.
\url{https://doi.org/10.1016/j.rama.2018.04.012}

\leavevmode\vadjust pre{\hypertarget{ref-donovan2018social}{}}%
Donovan, V. M., Burnett, J. L., Bielski, C. H., Birge, H. E., Bevans,
R., Twidwell, D., \& Allen, C. R. (2018). Social-ecological landscape
patterns predict woody encroachment from native tree plantings in a
temperate grassland. \emph{Ecology and Evolution}, \emph{8}(19),
9624--9632. \url{https://doi.org/10.1002/ece3.4340}

\leavevmode\vadjust pre{\hypertarget{ref-burnett2018thermal}{}}%
Burnett, J. L., Kevin, L. P., Wong, A., Allen, C. R., Haak, D. M.,
Stephen, B. J., \& Uden, D. R. (2018). Thermal tolerance limits of the
chinese mystery snail (bellamya chinensis): Implications for management.
\emph{American Malacological Bulletin}, \emph{36}(1), 140--144.

\leavevmode\vadjust pre{\hypertarget{ref-lasorte2018opportunities}{}}%
La Sorte, F. A., Lepczyk, C. A., Burnett, J. L., Hurlbert, A. H.,
Tingley, M. W., \& Zuckerberg, B. (2018). Opportunities and challenges
for big data ornithology. \emph{Condor}, \emph{120}(2), 414--426.
\url{https://doi.org/10.1650/CONDOR-17-206.1}

\leavevmode\vadjust pre{\hypertarget{ref-chuang2018enhancing}{}}%
Chuang, W. C., Garmestani, A., Eason, T. N., Spanbauer, T. L.,
Fried-Petersen, H. B., Roberts, C. P., Sundstrom, S. M., Burnett, J. L.,
Angeler, D. G., Chaffin, B. C., Gunderson, L., Twidwell, D., \& Allen,
C. R. (2018). Enhancing quantitative approaches for assessing community
resilience. \emph{Journal of Environmental Management}, \emph{213},
353--362. \url{https://doi.org/10.1016/j.jenvman.2018.01.083}

\leavevmode\vadjust pre{\hypertarget{ref-burnett2017range}{}}%
Burnett, J. L., Roberts, C. P., Allen, C. R., Brown, M. B., \& Moulton,
M. P. (2017). Range expansion by passer montanus in north america.
\emph{Biological Invasions}, \emph{19}(1), 5--9.
\url{https://doi.org/10.1007/s10530-016-1273-4}

\leavevmode\vadjust pre{\hypertarget{ref-allen2016avoiding}{}}%
Allen, C. R., Birge, H. E., Bartelt-Hunt, S., Bevans, R. A., Burnett, J.
L., Cosens, B. A., Cai, X., Garmestani, A. S., Linkov, I., Scott, E. A.,
Solomon, M. D., \& Uden, D. R. (2016). Avoiding decline: Fostering
resilience and sustainability in midsize cities. \emph{Sustainability},
\emph{8}(9). \url{https://doi.org/10.3390/su8090844}

\leavevmode\vadjust pre{\hypertarget{ref-burnett2016songbird}{}}%
Burnett, J. L., \& Sieving, K. E. (2016). Songbird distress calls as an
improved method for detecting red-shouldered hawks (buteo lineatus).
\emph{Florida Field Naturalist}, \emph{44}(4), 157--168.

\leavevmode\vadjust pre{\hypertarget{ref-burnett2015recent}{}}%
Burnett, J. L., \& Moulton, M. P. (2015). Recent trends in house sparrow
(passer domesticus) distribution and abundance in gainesville, alachua
county, florida. \emph{Florida Field Naturalist}, \emph{43}(4),
167--172.

\hypertarget{book-chapters}{%
\section{Book Chapters}\label{book-chapters}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-burnett2020introduced}{}}%
Burnett, J. L., \& Allen, C. R. (2020). Continental analysis of invasive
birds: North america. In C. T. Downs \& L. A. Hart (Eds.), \emph{Global
trends and impacts of alien invasive birds}. CABI, Wallingford, U.K.

\hypertarget{work-in-progress}{%
\section{Work in Progress}\label{work-in-progress}}

\hypertarget{selected-presentations}{%
\section{Selected Presentations}\label{selected-presentations}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-burnett2017perdix}{}}%
Burnett, J. L., Wszola, L., Mirochnitchenko, N., Stuber, Erica,
Bomberger Brown, M., \& Carroll, J. P. (2017). \emph{Gray partridge
distribution in north america: Changing landscapes and environment for
an introduced species}. 33rd International Congress of the International
Union of Game Biologists (IUGB).

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{primary-instructor}{%
\subsection{Primary Instructor}\label{primary-instructor}}

\begin{cventries}
    \cventry{Course design; weekly lectures; grading assignments and exams; office hours}{EDUC 391: Educational Psychology and Human Development}{09/2017 - 12/2017}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{graduate-student-instructor}{%
\subsection{Graduate Student
Instructor}\label{graduate-student-instructor}}

\begin{cventries}
    \cventry{Grading student essays and exams; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2020 - 04/2020}{}{}\vspace{-4.0mm}
    \cventry{Grading student essays and exams; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2019 - 04/2019}{}{}\vspace{-4.0mm}
    \cventry{Three review sessions per week; grading assignments and exams; office hours}{PSYCH 111: Introduction to Psychology}{01/2018 - 04/2018}{}{}\vspace{-4.0mm}
    \cventry{Grading student essays and exams; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2017 - 04/2017}{}{}\vspace{-4.0mm}
    \cventry{Three review sessions per week; grading assignments and exams; office hours}{PSYCH 240: Intro to Cognitive Psychology}{09/2016 - 12/2016}{}{}\vspace{-4.0mm}
    \cventry{Grading student essays and exams; office hours; supervising student research projects}{PSYCH 457 : Research in Educational and Cross-Cultural Settings}{01/2016 - 04/2016}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{program-assistant}{%
\subsection{Program Assistant}\label{program-assistant}}

\begin{cventries}
    \cventry{Supervising joint research projects between US and Chinese students; organizing student activities}{Global Course Connection: Beijing Normal University}{2015 - 2019}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{professional-service}{%
\section{Professional Service}\label{professional-service}}

\hypertarget{ad-hoc-reviewer}{%
\subsection{Ad Hoc Reviewer}\label{ad-hoc-reviewer}}

\begin{itemize}
\tightlist
\item
  Memory \& Cognition
\item
  NeuroImage
\item
  Visual Cognition
\item
  Cognitive Science
\item
  Scientific Studies of Reading
\item
  Frontiers in Psychiatry
\item
  Psychological Research
\end{itemize}

\hypertarget{references}{%
\section{References}\label{references}}

\begin{cventries}
    \cventry{Edward E. Smith Professor of Psychology and Neuroscience; Co-Director, functional MRI Center, University of Michigan; Senior Editor, Psychological Science}{John Jonides, Ph.D.}{jjonides@umich.edu; 734-764-0192}{}{}\vspace{-4.0mm}
    \cventry{Professor of Psychology and Education,  University of Michigan}{Kevin F. Miller, Ph.D.}{kevinmil@umich.edu; 734-615-1800}{}{}\vspace{-4.0mm}
    \cventry{Professor of Cognition \& Cognitive Neuroscience and Educational Psychology, University of Michigan}{Priti Shah, Ph.D.}{priti@umich.edu; 734-615-3745}{}{}\vspace{-4.0mm}
    \cventry{Professor of Psychology, University of Michigan}{Kai S. Cortina, Ph.D.}{schnabel@umich.edu; 734-615-3809}{}{}\vspace{-4.0mm}
\end{cventries}



\end{document}
